Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-11-12 manuscript/manuscript.tex
Fix editor's remark 8
Fix editor's remark 11

\noindent $f(r', \phi', \lambda')$ is the non-density dependent portion of the
integration kernels, $(r_i, \phi_j, \lambda_k)$ are the quadrature nodes, and
$W_i^r$, $W_j^\phi$, $W_k^\lambda$ are the quadrature weights.

@@

On the first iteration, the ratio $L_r/L_r^\text{orig} = 1$ because the tesseroid being
divided is the original one.
For future iterations, the ratio will be progressively smaller than one as the
tesseroids get smaller.
This is intended to limit the number of divisions to the ones that will
significantly reduce the numerical error:
dividing a large tesseroid with a small $\text{max}\{ \Delta \rho(r') \}$ would
improve the integration accuracy more than dividing a small tesseroid with a
higher $\text{max}\{ \Delta \rho(r') \}$.
We also do not divide tesseroids with $L_r < 1$ mm because any integration errors would
be negligible due to the small mass of the tesseroid..

>>>>

\noindent $f(r', \phi', \lambda')$ is the non-density dependent portion of the
integration kernels, $(r_i, \phi_j, \lambda_k)$ are the quadrature nodes, and
$W_i^r$, $W_j^\phi$, $W_k^\lambda$ are the quadrature weights.
The GLQ nodes and weights can be calculated as \citet[p.~391]{Hildebrand1987} (see
\citet{Uieda2016} for nodes and weights definitions on similar notation as this paper).

@@

On the first iteration, the ratio $L_r/L_r^\text{orig} = 1$ because the tesseroid being
divided is the original one.
For further iterations, the ratio will be progressively smaller than one as the
tesseroids get smaller.
This is intended to limit the number of divisions to the ones that will
significantly reduce the numerical error:
dividing a large tesseroid with a small $\text{max}\{ \Delta \rho(r') \}$ would
improve the integration accuracy more than dividing a small tesseroid with a
higher $\text{max}\{ \Delta \rho(r') \}$.
We also do not divide tesseroids with $L_r < 1$ mm because any integration errors would
be negligible due to the small mass of the tesseroid..
